%Rodolfo Rodriguez Alonso Resume
%Version 2 - 24/03/21
%Latex format

%hola mundo

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{graphicx}
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.49\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Rodolfo}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Rodriguez}}}}} % Last name
	
	\vspace{8pt}
	
	{\huge Computer Science Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.278\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{11}{Tlaquepaque Jal.}\\
	\icon{Whatsapp}{11}{3317205055}\\
	\icon{Linkedin}{11}{\href{https://www.linkedin.com/in/rodrodriguez2020/}{rodrodriguez2020}}\\

	\end{minipage}
\begin{minipage}[t]{0.350\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{At}{11}{\href{mailto:rod.rodriguez.2k21@gmail.com}{rod.rodriguez.2k21@gmail.com}}\\
	\icon{Github}{11}{\href{https://github.com/rodoro-2020}{rodoro-2020 resume}}\\
%	\icon{facebook}{12}{\href{https://www.facebook.com/Darknash.212}{Rod Rodriguez}}\\
\end{minipage}

\vspace{0.3cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.460\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	I have extensive experiencie as Windows and Linux OS sysadmin. I´m looking
	forward to joining a team where I can develop my skills and contribute professionally to achieve the goals. I´m
	always trying to improve my skills and knowledge so I can contribute with ideas in the best way to the company. \\ % Dummy text
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.43\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5}
		\baritem{Windows OS}{60}
		\baritem{Linux OS}{70}
		\baritem{Virtualization}{70}
		\baritem{Spectrum Scale}{40}
		\baritem{Scripting/Test Automation}{20}
	\end{barchart}
\end{minipage}

%\begin{center}
\begin{entrylist}
	%\bubbles{5/Self-taugt, 6/Teamwork, 4/Empathic, 3/Adaptability, 3/Blender}
	\bubbles{5/Self-taught} 
	\hspace{2mm} 
	\bubbles{5/Teamwork} 
	\hspace{2mm} 
	\bubbles{4/Adaptability}
	\hspace{2mm} 
	\bubbles{4/Empathic} 
	\hspace{2mm} 
	\bubbles{4/Responsibility}
\end{entrylist}
		
%\end{center}
%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{Jun 2012 -- Present}
		{Linux Test Engineer IBM Storage}
		{Kelly Services Mexico.}
			{{}\\$\bullet$ Linux RHEL and Windows Server OS System Administration.
				\\$\bullet$ Elastic Storage Server (ESS)/Spectrum Scale (GPFS) Support Engineer.
					\\$\bullet$ Basic programming in bash scripting and expect (TCL) lenguage for automation of tests for example:configurations and FW upgrades for Mellanox Switches and Linux operating system configurations.						
				\\$\bullet$Virtualization of computing resources with Vmware vsphere, vSphare Hypervisor, vCenter Server, Qemu/KVM/RHELV Linux.
				\\$\bullet$ On-site supports national and internacional clients for installation, configuration and consulting Security Network/hardening Windows/Linux RHEL Server for example:
				Bradesco Bank of brasil, ADO de Oriente, Corporativo The Home Depot Mexico, Grupo GEPP, Toshiba, Grupo modelo, Lenovo, Manpower,
				etc.
				\\$\bullet$ Basic use of containerization tools (Podman and Docker).			
				\\$\bullet$ GIT basic knowledge.
				\\$\bullet$ Installation and Configuration IBM Power Systems (Power 7 and 8, HMC)\\$\bullet$ Configuration of Storage Systems DS3000 Family,V7000, Flash Texas/Maverick Storage, Tivolli Storage Manager SW.\\}
	\entry
	{Jul 2011 -- Jun 2012}
	{IT Support}
	{RADEC SA de CV.}
	{{} \\$\bullet$ Team Lead technical IT support (Level 2). 
		\\$\bullet$ IT Network Support Level 2 infrastructure, based
		on Linux distro and Windos Server OS, Active Directory, GPO, SAMBA, DHCP, Firewall, FTP,
		NFS, HTTP servers.
		\\$\bullet$ IT support Level 2, for Windows 7 and macOS Leopard user desktop.
		\\$\bullet$ Preventive and corrective maintenance to IBM servers, PCs, notebook and macbook.\\$\bullet$ Installation and configuation of monitoring equipment (CCTV).\\}
	\entry
	{Jul 2009 -- Apr 2011}
		{Technical Support Manager}
	{Tec Smart SA. de CV. (Mr.Fix)}
	{{}\\$\bullet$ Team Lead technical support Level 2.
		\\$\bullet$ Installation, configuration and consulting of Windows and macoS OS, Microsoft Office, Antivirus and SW third party.
		\\$\bullet$ Preventive and corrective maintenance PCs, notebook and macbook.
		\\$\bullet$ Management of technical staff, preparation and presentation of inventory, sales, warranty and service reports for the 4 Mr. Fix Store in GDL. \\ \\}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}\\

\begin{entrylist}
	\entry
		{2003 -- 2007}
		{Bachelor's Degree}
		{Computer Science Engineer}
		{Universidad Tecnologica de Guadalajara-UTEG}
\end{entrylist}

\cvsect{SPECIALIZED TRAINING}\\

\begin{entrylist}
	\entry
		{2019}
		{Security Windows Server 2016}
		{Executrain}
		{}
\end{entrylist}

\begin{entrylist}
	\entry
	{2018}
	{Red Hat System administration II}
	{Executrain}
	{}
\end{entrylist}

\begin{entrylist}
	\entry
	{2018}
	{Identity with Windows Server 2016}
	{Executrain}
	{}
\end{entrylist}


\begin{entrylist}
	\entry
	{2018}
	{Installation Storage and Compute Windows Server 2016}
	{Executrain}
	{}
\end{entrylist}

\begin{entrylist}
	\entry
	{2011}
	{Gestion de LVM Linux OS}
	{ALEUX}
	{}
\end{entrylist}


%---------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.4\textwidth}	
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Languages}	

	$\bullet$ {Spanish} - native\\
	$\bullet$ {English} - B1 level - Studding currently\\


	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Hobbies}

		$\bullet$ Manga and Animation Japanese.\\
		$\bullet$ Football Soccer.\\  
		$\bullet$ Assemble lego figures with my kid.\\ 
		$\bullet$ Player Videogames in my Playstation 4.

\end{minipage}
%\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
